Temporal Graph Cube

### 2023-01-24 revision/response.tex

\item test

\end{itemize}

The point-to-point responses are given below.

\section{Response to Reviewer \#1}
\begin{Comments}
The expression of motivation is not clearly. Does the limitation of static graph cube is it cannot support range queries or it only can support latest data?
\end{Comments}
\noindent \textbf{Response:} [todo]. The major limitation of static graph cube is that it cannot support temporal multidimensional networks. Static graph cube can only be built on static multidimensional networks, e.g., DBLP where temporal information of co-authorships is omitted. Consequently, static graph cube cannot support range queries since there is no temporal information in its dataset. Static graph cube cannot support latest data because its authors didn't consider that new edges may be added into the static networks. Temporal graph cube supports latest data because we update the temporal networks and indexes when new edges are added.

### 2023-01-26 TemporalGraphCube/TemporalGraphCube_revision.tex
latex 1-26

\documentclass[10pt,journal,compsoc]{IEEEtran}
%\usepackage{ntheorem}
%\usepackage{algorithmic}
%\usepackage{cite}
%\usepackage{times}
\usepackage{amsmath,amsfonts,amssymb, amsthm, xspace}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{graphicx, subfigure,stfloats}
\usepackage{epstopdf}
\usepackage{textcomp}
\usepackage{ragged2e, xcolor}
\usepackage{balance}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{makecell}
\usepackage{url}
\usepackage{booktabs}

@@

Interestingly, we can avoid the problem of choosing an ideal $ A_i'' $ by adopting the partial materialization strategy \kw{MinLevel} \cite{zhao2011graph}, which we will discuss in Section~\ref{sec:partial_materialization}.
%
%Let's recall the time complexity of Algorithm~\ref{alg:temp_cuboid_baseline}: $ O(|\Vr|+\sum_{i=l-t_{base}}^{r-t_{base}}|\Sr[i]|+|S|) $, where $ \Vr $ and $ \Sr[i] $ are the node set and snapshot of the inputed temp-multi-network, $ S $ is the summarized snapshot of the inputed temp-multi-network. Our goal is to get the value of time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} with corresponding $ \Gr_i'' $ of each $ A_i'' $ as the inputed temp-multi-network in $ O(1) $ time and then choose the lowest time complexity and the corresponding $ \Gr_i'' $. We can not stand a higher time complexity to compute the time complexity of Algorithm~\ref{alg:temp_cuboid_baseline}, which will make the process of choosing an ideal $ \Gr_i'' $ unworthy compared to choosing a arbitrary $ \Gr_i'' $. In time complexity of Algorithm~\ref{alg:temp_cuboid_baseline}, . For our basic Algorithm~\ref{alg:temp_cuboid_baseline}, if we maintain a prefix array $ pArray $ for each precomputed $ \Gr_i'' $ of $ A_i'' $, in which
%\begin{equation}
%	\label{eqt:pre_array_baseline}
% 	pArray[i]=\sum_{j=1}^{i}|\Sr''[j]|, i \leq t_{end},
%\end{equation}
%$ \Sr''[j] $ is the snapshot at timestamp $ j+t_{base} $ as defined in Definition~\ref{def:snapshot}, we can easily compute the value of accumulation part ($ \sum_{i=l-t_{base}}^{r-t_{base}}|\Sr[i]| $) in the time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} by
%\begin{equation}
%	\label{eqt:pre_array_base_use}
%	pArray[r-t_{base}]-pArray[l-t_{base}-1].
%\end{equation}
%It is easy to update $ pArray $ and $ \Sr''[j] $ according to their definitions when adding new edges at the latest timestamp in each $ \Gr_i'' $ (we will talk about adding new edges into temporal graph cube in Section~\ref{subsec:growing}). As a result, we can compute the value of time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} with different $ \Gr_i'' $ as the inputed temp-multi-network by $ |\Vr_i''|+pArray[r-t_{base}]-pArray[l-t_{base}-1]+|S_i''| $ in $ O(1) $ time. .[not accurate because of $ |S_i''| $]

@@

\section{Related Work} \label{sec:related_work}
Our work extends data warehouse and OLAP techniques to temporal multidimensional networks. There are many works applying data warehouse and OLAP to other data types, such as stream data \cite{han2005stream}, spatio-temporal data \cite{gomez2009survey}, sequence data \cite{lo2008olap,liu2011cube}, and text data \cite{lin2008text}. Except the traditional relational data, Dehdouh et al. \cite{dehdouh2014columnar} tried to compute data cubes from column-oriented NoSQL data. As for graph data, except \cite{zhao2011graph}, some other works focus on heterogeneous networks \cite{yin2012hmgraph,wang2015tsmh}, but none of them focus on temporal multidimensional networks.

Our work is also related to graph summarization and analysis. For static graphs, there are some representative works, including graph compression with MDL (Minimum Description Length) principle \cite{navlakha2008graph}, attributed graph compression \cite{wu2014graph} and graph clustering based on vertices partitioning \cite{zhou2009graph}. Recently, there exist several studies on static graph summarization, such as summarizing directed acyclic graph (DAG) \cite{zhu2020top}, summarizing multi-relation graph \cite{ke2022multi} where multiple edges of different types may exist between any pair of vertices, and DPGS model \cite{zhou2021dpgs}, which can preserve properties like graph spectrum and the authorities and hubnesses of vertices especially in highly degree-skewed graphs while reconstructing graph. For temporal graph and dynamic graph, TimeCrunch \cite{shah2015timecrunch} summarizes a large dynamic graph with a set of important temporal structures using MDL, such as ranged full clique, periodic bipartite core, oneshot star, etc. \cite{fernandes2018dynamic,tsalouchidou2018scalable} investigate the problem of summarizing dynamic graph in real time, which use a sliding window of fixed length to summarize the latest snapshots. When a new snapshot is generated, the window slides forward, discarding the oldest snapshot in the window and generating a new summary. However, in this paper, we can specify arbitrary time window to query summarized result in real time. In addition, we summarize the graph based on the selected dimensions of vertices, while the previous studies summarize the graph based on the super-node and super-edge. MoSSo \cite{ko2020incremental} incrementally summarizes fully dynamic graph. The difference of \cite{ko2020incremental} with \cite{fernandes2018dynamic,tsalouchidou2018scalable} is that the edges in the graph are dynamically added and removed, and MoSSo incrementally summarizes the whole graph after any modification on the graph.

>>>>

\documentclass[10pt,journal,compsoc]{IEEEtran}
%\usepackage{ntheorem}
%\usepackage{algorithmic}
%\usepackage{cite}
%\usepackage{times}
\usepackage{amsmath,amsfonts,amssymb, amsthm, xspace}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{graphicx, subfigure,stfloats}
\usepackage{epstopdf}
\usepackage{textcomp}
\usepackage{ragged2e, xcolor}
\usepackage{balance}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{makecell}
\usepackage{url}
\usepackage{booktabs}
\usepackage{todonotes}

@@

Interestingly\todo{todo}, we can avoid the problem of choosing an ideal $ A_i'' $ by adopting the partial materialization strategy \kw{MinLevel} \cite{zhao2011graph}, which we will discuss in Section~\ref{sec:partial_materialization}.
%
%Let's recall the time complexity of Algorithm~\ref{alg:temp_cuboid_baseline}: $ O(|\Vr|+\sum_{i=l-t_{base}}^{r-t_{base}}|\Sr[i]|+|S|) $, where $ \Vr $ and $ \Sr[i] $ are the node set and snapshot of the inputed temp-multi-network, $ S $ is the summarized snapshot of the inputed temp-multi-network. Our goal is to get the value of time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} with corresponding $ \Gr_i'' $ of each $ A_i'' $ as the inputed temp-multi-network in $ O(1) $ time and then choose the lowest time complexity and the corresponding $ \Gr_i'' $. We can not stand a higher time complexity to compute the time complexity of Algorithm~\ref{alg:temp_cuboid_baseline}, which will make the process of choosing an ideal $ \Gr_i'' $ unworthy compared to choosing a arbitrary $ \Gr_i'' $. In time complexity of Algorithm~\ref{alg:temp_cuboid_baseline}, . For our basic Algorithm~\ref{alg:temp_cuboid_baseline}, if we maintain a prefix array $ pArray $ for each precomputed $ \Gr_i'' $ of $ A_i'' $, in which
%\begin{equation}
%	\label{eqt:pre_array_baseline}
% 	pArray[i]=\sum_{j=1}^{i}|\Sr''[j]|, i \leq t_{end},
%\end{equation}
%$ \Sr''[j] $ is the snapshot at timestamp $ j+t_{base} $ as defined in Definition~\ref{def:snapshot}, we can easily compute the value of accumulation part ($ \sum_{i=l-t_{base}}^{r-t_{base}}|\Sr[i]| $) in the time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} by
%\begin{equation}
%	\label{eqt:pre_array_base_use}
%	pArray[r-t_{base}]-pArray[l-t_{base}-1].
%\end{equation}
%It is easy to update $ pArray $ and $ \Sr''[j] $ according to their definitions when adding new edges at the latest timestamp in each $ \Gr_i'' $ (we will talk about adding new edges into temporal graph cube in Section~\ref{subsec:growing}). As a result, we can compute the value of time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} with different $ \Gr_i'' $ as the inputed temp-multi-network by $ |\Vr_i''|+pArray[r-t_{base}]-pArray[l-t_{base}-1]+|S_i''| $ in $ O(1) $ time. .[not accurate because of $ |S_i''| $]

@@

\section{Related Work} \label{sec:related_work}
Our work extends data warehouse and OLAP techniques to temporal multidimensional networks. There are many works applying data warehouse and OLAP to other data types, such as stream data \cite{han2005stream}, spatio-temporal data \cite{gomez2009survey}, sequence data \cite{lo2008olap,liu2011cube}, and text data \cite{lin2008text}. Except the traditional relational data, Dehdouh et al. \cite{dehdouh2014columnar} tried to compute data cubes from column-oriented NoSQL data. As for graph data, except \cite{zhao2011graph}, some other works focus on heterogeneous networks \cite{yin2012hmgraph,wang2015tsmh}. \revision{\cite{wang2014pagrol,chen2020high} improve efficiency of graph OLAP query by parallelization and distribution}. However, none of them focus on temporal multidimensional networks.

Our work is also related to graph summarization and analysis. For static graphs, there are some representative works, including graph compression with MDL (Minimum Description Length) principle \cite{navlakha2008graph}, attributed graph compression \cite{wu2014graph} and graph clustering based on vertices partitioning \cite{zhou2009graph}. Recently, there exist several studies on static graph summarization, such as summarizing directed acyclic graph (DAG) \cite{zhu2020top}, summarizing multi-relation graph \cite{ke2022multi} where multiple edges of different types may exist between any pair of vertices, and DPGS model \cite{zhou2021dpgs}, which can preserve properties like graph spectrum and the authorities and hubnesses of vertices while reconstructing graph. \revision{However, all of them ignore the temporal information of big graph data}. For temporal graph and dynamic graph, TimeCrunch \cite{shah2015timecrunch} summarizes a large dynamic graph with a set of important temporal structures using MDL, such as ranged full clique, periodic bipartite core, oneshot star, etc. \revision{Some works summary graph streams into one sketche, e.g., \cite{mudannayake2021kmatrix,tang2016graph,ma2021parameter,ashrafi2021gs4,gou2019fast,chen2022scube}. \cite{fernandes2018dynamic,tsalouchidou2018scalable} use a sliding window of fixed length to only summarize the latest snapshots, and \cite{ko2020incremental} only summa}. However, in this paper, we can specify arbitrary time window to query summarized result in real time. In addition, we summarize the graph based on the selected dimensions of vertices, while the previous studies summarize the graph based on the super-node and super-edge. MoSSo \cite{} incrementally summarizes fully dynamic graph. The difference of \cite{ko2020incremental} with \cite{fernandes2018dynamic,tsalouchidou2018scalable} is that the edges in the graph are dynamically added and removed, and MoSSo incrementally summarizes the whole graph after any modification on the graph.
